Transmembrane helices are an overlooked and evolutionarily conserved source of major histocompatibility complex class I and II epitopes

### 2021-12-12 frontiers.tex
Add abstract, progress #263

%%% Leave the Abstract empty if your article does not require one, please see the Summary Table for full details.
\section{}
For full guidelines regarding your manuscript please refer to \href{http://www.frontiersin.org/about/AuthorGuidelines}{Author Guidelines}.

As a primary goal, the abstract should render the general significance and conceptual advance of the work clearly accessible to a broad readership. References should not be cited in the abstract. Leave the Abstract empty if your article does not require one, please see \href{http://www.frontiersin.org/about/AuthorGuidelines#SummaryTable}{Summary Table} for details according to article type.

>>>>

%%% Leave the Abstract empty if your article does not require one, please see the Summary Table for full details.
\section{}
Cytolytic T cell responses are predicted to be biased towards membrane proteins. 
The peptide-binding grooves of most alleles
of histocompatibility complex class I (MHC-I) are relatively hydrophobic, 
therefore peptide fragments derived from human transmembrane helices (TMHs) are predicted to be presented more often as would be expected 
based on their abundance in the proteome. However, the physiological reason of why membrane proteins might be over-presented is unclear. 
In this study, we show that the predicted over-presentation of TMH-derived peptides is general, as it is predicted for bacteria and viruses 
and for both MHC-I and MHC-II, and confirmed by re-analysis of epitope databases. Moreover, we show that TMHs are evolutionarily more conserved, 
because single nucleotide polymorphisms (SNPs) are present 
relatively less frequently in TMH-coding chromosomal regions 
compared to regions coding for extracellular and cytoplasmic protein regions. 
Thus, our findings suggest that 
both cytolytic and helper T cells are more tuned to respond to membrane proteins, 
because these are evolutionary more conserved. 
We speculate that TMHs are less prone to mutations 
that enable pathogens to evade T cell responses.
